---
title: "Developing Data Products - Week 4 Assignment"
author: "Rick M"
date: "2/25/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Week 4 Project

- This is a for the week four project for Developing Data Products where we were to create a shinny application.  
- I used the mtCars dataset to look at hour transmission, number of cylinders, and number of gears impacted fuel economy in the dataset. 
- The link to the Shiny app can be found here: https://ricm.shinyapps.io/Developing_Data_Products_Week_4_Assignment/
- The link to the code can be found here: https://github.com/ricmaur/DevDataProdWeek4

## Overview

The shinny application uses plotly to graph fuel economy (MPG) against different variables

```{r}
head(mtcars)
```

## Server Code

```{r echo=TRUE, warning=FALSE, message=FALSE, eval=FALSE}
library(shiny)
library(plotly)
mpgData <- mtcars
mpgData$am <- factor(mpgData$am, labels = c("Automatic", "Manual"))
shinyServer(function(input, output) {
    formulaText <- reactive({
        paste("MPG vs ", input$variable)
    })
    output$caption <- renderText({
        formulaText()
    })
    output$mpgPlot <- renderPlot({
        ggplot(mpgData, aes_string(y=input$variable, x="mpg")) + geom_point()
    })
})
```

## UI Code

```{r echo=TRUE, warning=FALSE, message=FALSE, eval=FALSE}
library(shiny)
shinyUI(fluidPage(
    titlePanel("mtcars Dataset - Miles per Gallon"),
    sidebarPanel(
        selectInput("variable", "Select an option to see how various factors impact MPG:", 
                    c("Cylinders" = "cyl",
                      "Transmission" = "am",
                      "Gears" = "gear"))
    ),
    mainPanel(
        h3(textOutput("caption")),
        plotOutput("mpgPlot")
    )
))
```

